The impact of information about tobacco-related reproductive vs. general health risks on South Indian women's tobacco use decisions

### 2020-11-06 paper.Rmd
Added affiliations and acknowledgements section

---
title: The impact of information about tobacco-related reproductive vs. general health risks on South Indian women's tobacco use decisions
author: Caitlyn D. Placek, Renee E. Magnan, Vijaya Srinivas, Poornima Jaykrishna, Kavitha Ravi, Anisa Khan, Purnima Madhivanan and Edward H. Hagen
output: 
  bookdown::html_document2:
    toc: false
    toc_depth: 2
    number_sections: false
always_allow_html: true
csl: apa.csl
bibliography: mysore_tobacco2016.bib
---

@@

All analyses were conducted in `r R.version.string`. Data are available here: https://doi.org/10.5281/zenodo.3987496

@@

>>>>

---
title: The impact of information about tobacco-related reproductive vs. general health risks on South Indian women's tobacco use decisions
output: 
  bookdown::html_document2:
    toc: false
    toc_depth: 2
    number_sections: false
always_allow_html: true
csl: apa.csl
bibliography: mysore_tobacco2016.bib
---

#### Caitlyn D. Placek^1^, Renee E. Magnan^2^, Vijaya Srinivas^3^, Poornima Jaykrishna^3^, Kavitha Ravi^3^, Anisa Khan^3^, Purnima Madhivanan^3,4,5,6^ and Edward H. Hagen^7,^*

^1^Department of Anthropology, Ball State University, Muncie, IN

^2^Department of Psychology, Washington State University, Vancouver, WA

^3^Public Health Research Institute of India, Mysore, Karnataka, India

^4^Department of Health Promotion Sciences, Mel & Enid Zuckerman College of Public Health, University of Arizona, Tucson, Arizona

^5^Division of Infectious Diseases, College of Medicine, University of Arizona, Tucson, Arizona

^6^Department of Family & Community Medicine, College of Medicine, University of Arizona, Tucson, Arizona

^7^Department of Anthropology, Washington State University, Vancouver, WA

*Please address correspondence to Edward H. Hagen, Department of Anthropology, Washington State University, Vancouver, WA 98686. Phone number: 360-546-9257, email: edhagen@wsu.edu

@@

All analyses were conducted in `r R.version.string`. Code is available here: https://github.com/grasshoppermouse/mysore2016tobacco. Data are available here: https://doi.org/10.5281/zenodo.3987496

@@

## Acknowledgements

We would like to thank our participants for their engagement in the study and staff from the Public Health Research Institute of India for assisting with data collection.

## Author contributions

CDP and EHH conceived of the study. CDP, REM, and EHH designed the study. CDP, VS, PJ, KR, AK, and PM carried out the study. CDP and EHH analyzed the data and wrote the initial draft of the paper. All authors contributed to the final draft of the paper.

## Financial support

Funding was provided by the Washington State University Meyer Award and the Washington State University Vancouver Mini Grant to EHH and CDP; startup funds to CDP from Ball State University; and PM was partially funded by the National Institutes for Health grants # R15-AI128714-01 and D43 TW010540.

## Conflicts of interest

CDP, REM, VS, PJ, KR, AK, PM, and EHH declare none.

## Research Transparency and Reproducibility

Data analysis code, presentation slides, and questionnaires are available here: https://github.com/grasshoppermouse/mysore2016tobacco. Data are archived here: https://doi.org/10.5281/zenodo.3987496
